Deep Reinforcement Learning for Conservation Decisions

### 2022-01-31 manuscript/manuscript.Rmd
Update manuscript/manuscript.Rmd
Co-authored-by: mlap <marcuslapeyrolerie@me.com>

We do recognize the need for more complex, "precise" models to derive quanitatively precise management policy in specific management problems such as fisheries, forestry, or climate change mitigation efforts. 
The examples here should provide ecologists with a greater background to engage in the collaborative development of such methods, while also highlighting challenges which ecological problems pose to existing techniques.
Even the simple models we consider here contain many sources of complexity -- significant stochasticity, non-linear dynamics, hysteresis -- that are likely commonplace to ecological problems but have not been well represtented in RL research to date. 
Such work is beyond the scope of any one paper: it will require not only more computational resources, but more collaborations between large teams of ecologists and computer scientists.

>>>>

We do recognize the need for more complex, "precise" models to derive quanitatively precise management policy in specific management problems such as fisheries, forestry, or climate change mitigation efforts. 
The examples here should provide ecologists with a greater background to engage in the collaborative development of such methods, while also highlighting challenges which ecological problems pose to existing techniques.
Even the simple models we consider here contain sources of complexity such as hysteresis that are likely commonplace to ecological problems but have not been well represented in RL research to date. 
Such work is beyond the scope of any one paper: it will require not only more computational resources, but more collaborations between large teams of ecologists and computer scientists.
